Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-23 Draft/input.tex
removed some notes by BJ in the input section (discussed in the email thread), added HSS and RF as authors

The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five flavour scheme, NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
Since this PDF set has no photonic density, photon-induced processes are not considered.
\BJ{I would change that sentence to simply {\em Photon-induced processes are not considered.}, as there are more reasons for disregarding the photon-induced contributions. } 
Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
\BJ{Should we say something about singularities due to soft photon exchange in the $t$-channel that are removed in VBFNLO and POWHEG by a technical cutoff?}
Note that no bottom-quark induced processes are included.
They would lead to top quarks in the final state which have a different experimental signature than two light jets, missing transverse energy, and two positively charged leptons.

>>>>

The hadronic scattering processes are simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$.
The NNPDF~3.0 parton distribution functions~(PDFs)~\cite{Ball:2014uwa} with five massles flavour,\footnote{
For the process considered, no bottom (anti-)quarks appear in the initial or final state at LO and NLO.} 
NLO-QCD evolution, and a strong coupling constant $\alphas\left( \MZ \right) = 0.118$ are employed.\footnote{The corresponding identifier {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.}
%Since this PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised according to the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.
